---
title: "Visualise SOFUN"
author: "Beni Stocker"
date: "2/2/2021"
output: html_document
---

```{r setup, include=FALSE}
library(ggplot2)
library(dplyr)
library(rbeni)
```

This illustrates some common functionalities for reading and plotting NetCDF files in general and SOFUN outputs specifically. Functions are implemented by the [rbeni R package, available from GitHub](https://github.com/stineb/rbeni).

## Read output

Set directory where output is located. Output is written by SOFUN to `./output_nc`.
```{r}
dir <- "~/data/sofun_outputs/global_FULL_MODIS-C006_MOD15A2_v3.4/"
```

Annual

```{r}
nc_gpp <- read_nc_onefile(paste0(dir, "global_FULL_MODIS-C006_MOD15A2_v3.4.a.gpp.nc"),  varnam = "gpp")
nc_pet <- read_nc_onefile(paste0(dir, "global_FULL_MODIS-C006_MOD15A2_v3.4.a.pet.nc"),  varnam = "pet")
nc_alpha <- read_nc_onefile(paste0(dir, "global_FULL_MODIS-C006_MOD15A2_v3.4.a.alpha.nc"),  varnam = "alpha")
```

Daily: Take mean over daily values and read file.

```{r}
nc_wcont <- nc_timmean(paste0(dir,  "global_FULL_MODIS-C006_MOD15A2_v3.4.d.wcont.nc"))

## providing argument return_ofil writes to file, separate step for reading
system(paste0("cdo timmean ", dir, "global_FULL_MODIS-C006_MOD15A2_v3.4.d.vpd.nc ", dir, "global_FULL_MODIS-C006_MOD15A2_v3.4.a.vpd.nc"))
nc_vpd <- read_nc_onefile(paste0(dir, "global_FULL_MODIS-C006_MOD15A2_v3.4.a.vpd.nc"),  varnam = "vpd") %>% 
  nc_selyear(2010)
```

## Global maps

Annual

```{r}
plot_map3(nc_gpp, varnam = "gpp", colorscale = viridis::cividis)
plot_map3(nc_pet, varnam = "pet", colorscale = viridis::cividis)
plot_map3(nc_alpha, varnam = "alpha", colorscale = viridis::cividis)
# plot_map3(nc_wcont, varnam = "wcont", colorscale = viridis::cividis)

plot_map3(nc_vpd, varnam = "vpd", colorscale = viridis::cividis, plot_title = "VPD", plot_subtitle = "Annual mean", legend_title = "(Pa)", latmin = -60, latmax = 85)
ggsave("~/sofun/fig/vpd_map.pdf", width = 8, height = 6)
```

## Integrate globally

```{r}
df <- integrate_lonlat(paste0(dir,  "global_FULL_MODIS-C006_MOD15A2_v3.4.2000.a.gpp.nc"),  
                       paste0(dir,  "global_FULL_MODIS-C006_MOD15A2_v3.4.fland.nc"), 
                       varnam = "gpp")

df <- integrate_lonlat(paste0(dir,  "global_FULL_MODIS-C006_MOD15A2_v3.4.a.vpd.nc"),  
                       paste0(dir,  "global_FULL_MODIS-C006_MOD15A2_v3.4.fland.nc"), 
                       varnam = "vpd")
```

And plot.
```{r}
df %>% 
  ggplot(aes(x = date, y = vpd)) +
  geom_line() +
  labs(title = "VPD", subtitle = "Global mean, based on WATCH-WFDEI climate reanalysis data", y = "VPD (Pa)", x = "Year")
ggsave("~/sofun/fig/vpd_globalmean.pdf", width = 6, height = 4)
```
